---
title: "Index"
author: "Joshua Lansing"
date: "May 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
source("analysis.R")
```
## Summary information
The data was provided by [Shooting Tracker](http://www.shootingtracker.com/).
There were a total of `r num_shootings` in 2018. `r lives_lost` lives were lost
that year. `r city_most_impacted` suffered the most casualties (injured and 
killed). `r state_most_impacted` was the state that suffered the most 
casualties. And `r state_least_impacted` suffered the least amount of 
casualties.

## Summary Table
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
kable(summary_table)
```

By and large, we can see from this table, at least by state, the number of
those injured is larger than those killed. In fact, only two states has a
higher amount of people killed than injured. We can also see that the most
casualties appear to happen in states with highest in states known for having
higher populations (eg. California, Florida).

## Description of a particular incident
On `r cal_date`, a terrible shooting occurred at `r cal_address` in southern
California. According to [USA Today](https://www.usatoday.com/story/news/2018/11/08/mass-shooting-borderline-bar-grill-thousand-oaks-southern-california/1927840002/), `r cal_killed` were killed, and 
`r cal_injured` were injured. This totals to `r cal_killed + cal_injured`
casualties.

## Interactive map
This map is used to visually view the location of shootings, as well as their
magnitude by number of casualties.
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
map_plot
```
Here we see that most of the shootings occur in the south-eastern parts of the
US. We can also see the severity (number of casualties) appears to go up as the
size of the cities goes up.

## Plot of Choice
I decided to ask myself "Were there months throughout 2018 that had more
or less shooting casualties than others?"

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
casualties_per_month
```

The chart shows that significantly more shootings happened in June and July
than in other months. I also found it interesting that the least amount of
shootings occurred in December. I can't say much for sure, considering this is
only showing shootings from 2018, but perhaps shooting rates change with
travelling seasons. 
i.e: People usually travel more in the summer, and people are more likely to
stay home, or travel differently for the holidays in the winter.
